---
title: "Flood frequency analysis  <font size=5>v. 1.0</font>"
author: "Water Resources Unit, NAHRIM"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: lumen
    css: bootstrap.css
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: true
bibliography: references.bib
link-citations: true
params:
  Station_No: 
    label: "Station number"
    input: text
    value: "3116430"
  Station_Name: 
    label: "Station name"
    input: text
    value: "Sg Klang di Jambatan Sulaiman"
  SF_filename: 
    label: "Annual maximum series or daily peak flow in csv (Date, Flow) - Date format dd/mm/yyyy"
    input: file
    value: "OSU_peak.csv"
  Water_year_month:
    label: "Water year starts from month (if any, default is 1)"
    input: numeric
    value: 10
    min: 1
    max: 12
    step: 1
  Flood_AEP:
    label: "Find Annual Exceedance Probability (AEP) or return period given flood value (m^3/s)"
    input: numeric
    value: 41971
    min: 0
  Data_source: 
    label: "Data source"
    input: text
    value: "JPS"
---

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover(); 
});
</script>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning=FALSE, 
                      message=FALSE,
                      fig.align = 'center')
```

# Introduction

This Rmarkdown interactive document was created for flood frequency analysis. 

Most of the methods used in this analysis is in accordance with **Guidelines for Determining Flood Flow Frequency - Bulletin 17C ** by US Geological Survey [@england_jr_guidelines_2019]. 



```{r input, warning=FALSE, message=FALSE, echo=FALSE}

library(lfstat)
library(tidyverse)
library(lubridate)
library(lmom)
library(Metrics)
library(smwrBase)

library(ggplot2)
library(plotly)
library(scales)
library(kableExtra)
library(reactable)

library(openxlsx)
library(extrafont)

###################
#installation of USGS packages

#remotes::install_github("USGS-R/smwrData")
#remotes::install_github("USGS-R/smwrBase")

# set strings as factors to false
options(stringsAsFactors = FALSE)

###################
# INPUT DATA

#streamflow data
station_no <- params$Station_No
station_name <- params$Station_Name

#set filename
filename2 <- paste0("FFA", station_no, "_", station_name)

#station streamflow data path in working dir
sf_filename <- params$SF_filename

#water year, start month
#if no water year, set 1 (Jan)
water_yr_mth <- params$Water_year_month

#flood value
flood_value <- params$Flood_AEP


#chart subtitle
chart_subtitle <- paste0("Station ", station_no, ": ", station_name)

#chart caption
data_source <- params$Data_source
chart_caption <- paste0("Data source: ", data_source)


#version no
version_no <- "Flood frequency analysis 1.0"


#new directory to save output files
#new_dir <- tempdir() #for shiny
new_dir <- filename2  #for standalone rmd


font_family <- "Roboto"


#database file path (if any)
#db_path <- "F:/Documents/2020/20200604_SF_PM/Data/SF_1d_avg/SF_1d_avg_PM_all_clean1.csv"
db_path <- "C:/Users/user/Documents/GYC/FDC/Data/SF_1d_avg_PM_20200720_clean1.csv"



```

The streamflow station number is **`r station_no`**, **`r station_name`**.

The source of data is from **`r data_source`**. 

```{r working_dir, eval=TRUE}
#set working directory if standalone rmd, false if shiny

# get current working directory
working_dir <- getwd()
dir.create(filename2)
setwd(filename2)


#font
#font_import(pattern="Roboto", prompt=FALSE)
#windowsFonts(sans="Roboto")
#loadfonts(device="win")
#loadfonts(device="postscript")


```


```{r single_stn, eval=TRUE}

#run this code if streamflow data is from single station
###########################
##OPTIONS (streamflow station data or from database) #############
# peak annual/daily? flow data

#input format in c(Date, Flow) in csv (case sensitive), station_no is station number, Flow in m3/s

flowdata <- read.csv(file = paste0(sf_filename),
                     #skip = 1,  #skip = 1 if csv from TIDEDA
                     header = TRUE, sep=",") #depends on working dir

```


```{r database, eval=FALSE}

#run this code if streamflow data is from database
#from streamflow database

flow_db <- read.csv(file = db_path, header = TRUE, sep=",")

flowdata <- flow_db %>%
  filter(Stn_no == station_no) %>% #check field name
  select(Date, Flow) %>%
  arrange(Date)

```


```{r prepare_data, warning=FALSE, message=FALSE, echo=FALSE}

#rename columns
colnames(flowdata)[1:2] <- c("Date", "Flow")

#reformat columns
flowdata$Date <- as.Date(flowdata$Date, format = "%d/%m/%Y")
flowdata$Flow <- as.numeric(as.character(flowdata$Flow))


#year with data
year_w_data <- nrow(flowdata)


# add columns for data aggregation
## add a year column to data.frame
flowdata <- flowdata %>%
  mutate(year = year(Date))
## add a month column to data.frame
flowdata <- flowdata %>%
  mutate(month = month(Date))
## add a day column to data.frame
flowdata <- flowdata %>%
  mutate(day = day(Date))


# CREATE LF OBJECT
#rename column
flowdata <- flowdata %>% 
  rename(flow = "Flow")

lf_data <- createlfobj(flowdata, 
                       hyearstart = water_yr_mth, #start of hydrological year
                       baseflow = T)

# define data unit
setlfunit("m^3/s")
flowunit(lf_data) <- "m^3/s"

#rename column back
flowdata <- flowdata %>% 
  rename(Flow = "flow")

###################

## select data
flowdata_sel <- flowdata


###################
# Maximum annual flow

#flowdata_sel_max <- flowdata_sel %>%
#  group_by(year) %>%
#  summarise(max_Q = max(Flow, na.rm = T),
#            Max_date = Date[which.max(Flow)])

flowdata_sel_max <- lf_data %>%
  group_by(hyear) %>%
  summarise(max_Q = max(flow, na.rm = T),
            Max_date = year[which.max(flow)]) %>% 
  rename(year = hyear)

```


```{r fit_distributions}

#PLOTTING POSITION - WEIBULL
#record length in years (n)
n_yrs_min <- nrow(flowdata_sel_max)

Q_pp <- flowdata_sel_max %>% 
  arrange(-max_Q) %>%
  mutate(rank = rank(-max_Q, ties.method= "first"), 
         plot_p = rank/(n_yrs_min + 1),
         ret_p = (n_yrs_min + 1)/rank) %>% # plotting position
  rename(Year = year,
         Q = max_Q)

#vector of return periods
rp <- c(2, 5, 10, 25, 50, 100, 200)

#vector of distributions
#selected distributions 
dist_lf <- c("ln3", "pe3", "wei", "gev", "gum", "glo", "nor")


#FITTING DISTRIBUTIONS
#use lfstat for fitting distributions
evfit.fxd <- evfit(flowdata_sel_max$max_Q, distribution = dist_lf,
                   extreme = "maximum", zeta = 0) #so results same as hydrognomon


q.evfit.fxd <- evquantile(evfit.fxd, return.period = rp)

#extract quantile results
qT.evfit.fxd <- data.frame(q.evfit.fxd[["T_Years_Event"]])
qT.evfit.fxd <- as_data_frame(qT.evfit.fxd, rownames = "RP")
qT.evfit.fxd$RP <- as.numeric(as.character(qT.evfit.fxd$RP))

#extract parameters
q.evfit.fxd.param <- q.evfit.fxd$parameters

###################
## Log-Pearson III


# estimate moments
moments = samlmu(Q_pp$Q, sort.data = TRUE)
log.moments <- samlmu(log(Q_pp$Q), sort.data = TRUE )

# estimate parameters
parLPE3 <- pelpe3(log.moments) # log Pearson

# estimate 1:100 yr event (0.01 probability)
LogPE3 = exp(quape3(0.99, parLPE3))



#extract parameters into list
lpe3_param_list <- list(parLPE3[["mu"]], parLPE3[["sigma"]], parLPE3[["gamma"]])


# add results to quantile table - package smwrBase
qT.evfit.fxd <- qT.evfit.fxd %>%
  mutate(lpe3 = qlpearsonIII((1-1/RP), 
                             parLPE3[["mu"]], parLPE3[["sigma"]], parLPE3[["gamma"]]))


```

# Flood Frequency Curve

```{r static_chart_ffc, fig.show = 'hide'}

#COMPARISON OF ALL DISTRIBUTIONS IN PROBABILITY PLOT
#for log axis
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))


# round y axis limit
log_upper <- 10^(ceiling(log10(max(Q_pp$Q)*1.1)))
log_lower <- 10^(floor(log10(min(Q_pp$Q)*0.9)))


#chart
#unable to change x-axis from non- exceedance to exceedance

#log chart
Q_prob_plot_log <- Q_pp %>%
  ggplot(aes(x = (1-plot_p), y = Q)) +
  geom_point(aes(x = (1-plot_p), y = Q, color = "Empirical"),
             shape = 16, size = 1.5) +
  stat_function(fun = qua_ev, args = list(distribution = "gev", 
                                          para = q.evfit.fxd.param$gev), 
                aes(color = "GEV (max) - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quaglo, args = list(unname(q.evfit.fxd.param$glo)), 
                aes(color = "GLO"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = qua_ev, args = list(distribution = "gum", 
                                          para = q.evfit.fxd.param$gum), 
                aes(color = "Gumbel (EV I - max) - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = qualn3, args = list(unname(q.evfit.fxd.param$ln3)), 
                aes(color = "Lognormal"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quape3, args = list(unname(q.evfit.fxd.param$pe3)), 
                aes(color = "Pearson Type III"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quawei, args = list(unname(q.evfit.fxd.param$wei)), 
                aes(color = "Weibull (EV III) - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quanor, args = list(unname(q.evfit.fxd.param$nor)), 
                aes(color = "Normal - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  #stat_function(fun = quaLPE3, args = list(parLPE3), 
  stat_function(fun = qlpearsonIII, args = lpe3_param_list, 
                aes(color = "Log Pearson III"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  theme_bw(base_size = 10) +
  scale_x_log10(
    name = "Non-exceedance probability", 
    breaks = breaks, minor_breaks = minor_breaks,
    limits = c(0.01, 1),
    sec.axis = sec_axis(trans = ~((1-.)*100), 
                        name = "Annual Exceedance Probability, AEP (%)",
                        breaks = c(99,98,95,90,80,70,60,50,20,1),
                        labels = c(99,98,95,90,80,70,60,50,20,1)
                        )
  ) + 
  scale_y_log10(name = bquote("Annual peak flow "~(m^3/s)), 
                breaks = breaks, minor_breaks = minor_breaks,
                limits = c(log_lower, log_upper), #adjust limits accordingly
                labels = scales::number_format(accuracy = 1)
  ) +
  scale_colour_manual("Distributions",
                      values = c("Empirical" = "black", 
                                 "Pearson Type III" = "blue2",
                                 "Log Pearson III" = "purple",
                                 "Normal - LM" = "maroon3",
                                 "Lognormal" = "orange", 
                                 "Gumbel (EV I - max) - LM" = "magenta",
                                 "GEV (max) - LM" = "red", 
                                 "Weibull (EV III) - LM" = "cyan3",
                                 "GLO" = "green3"
                                 )) +
  theme(text=element_text(family=font_family, 
                          color="grey20", 
                          size = 10),
        axis.title = element_text(size = 8, colour = "gray35"),
        legend.position = "right") +
  labs(title = paste0("Flood frequency curve"),
       subtitle = paste0(chart_subtitle),
       caption = paste0(chart_caption))

Q_prob_plot_log

#print last plot to file
ggsave(paste0(new_dir, "/", filename2, "_flood_freq_log.jpg"), dpi = 300,
       width = 7.52, height = 4.56, units = "in")


# y axis limit
y_upper <- max(Q_pp$Q)*1.1
y_lower <- min(Q_pp$Q)*0.9



#normal chart
Q_prob_plot <- Q_pp %>%
  ggplot(aes(x = (1-plot_p), y = Q)) +
  geom_point(aes(x = (1-plot_p), y = Q, color = "Empirical"),
             shape = 16, size = 1.5) +
  stat_function(fun = qua_ev, args = list(distribution = "gev", 
                                          para = q.evfit.fxd.param$gev), 
                aes(color = "GEV (max) - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quaglo, args = list(unname(q.evfit.fxd.param$glo)), 
                aes(color = "GLO"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = qua_ev, args = list(distribution = "gum", 
                                          para = q.evfit.fxd.param$gum), 
                aes(color = "Gumbel (EV I - max) - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = qualn3, args = list(unname(q.evfit.fxd.param$ln3)), 
                aes(color = "Lognormal"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quape3, args = list(unname(q.evfit.fxd.param$pe3)), 
                aes(color = "Pearson Type III"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quawei, args = list(unname(q.evfit.fxd.param$wei)), 
                aes(color = "Weibull (EV III) - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quanor, args = list(unname(q.evfit.fxd.param$nor)), 
                aes(color = "Normal - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  #stat_function(fun = quaLPE3, args = list(parLPE3), 
  stat_function(fun = qlpearsonIII, args = lpe3_param_list, 
                aes(color = "Log Pearson III"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  theme_bw(base_size = 10) +
  scale_x_log10(
    name = "Non-exceedance probability", 
    breaks = breaks, minor_breaks = minor_breaks,
    limits = c(0.01, 1),
    sec.axis = sec_axis(trans = ~((1-.)*100), 
                        name = "Annual Exceedance Probability, AEP (%)",
                        breaks = c(99,98,95,90,80,70,60,50,20,1),
                        labels = c(99,98,95,90,80,70,60,50,20,1)
    )
  ) + 
  scale_y_continuous(name = bquote("Annual peak flow "~(m^3/s)), 
                     limits = c(y_lower, y_upper), #adjust limits accordingly
                     labels = scales::number_format(accuracy = 1)
  ) +
  scale_colour_manual("Distributions",
                      values = c("Empirical" = "black", 
                                 "Pearson Type III" = "blue2",
                                 "Log Pearson III" = "purple",
                                 "Normal - LM" = "maroon3",
                                 "Lognormal" = "orange", 
                                 "Gumbel (EV I - max) - LM" = "magenta",
                                 "GEV (max) - LM" = "red", 
                                 "Weibull (EV III) - LM" = "cyan3",
                                 "GLO" = "green3"
                      )) +
  theme(text=element_text(family=font_family, 
                          color="grey20", 
                          size = 10),
        axis.title = element_text(size = 8, colour = "gray35"),
        legend.position = "right") +
  labs(title = paste0("Flood frequency curve"),
       subtitle = paste0(chart_subtitle),
       caption = paste0(chart_caption))

Q_prob_plot


#print last plot to file
ggsave(paste0(new_dir, "/", filename2, "_flood_freq.jpg"), dpi = 300,
       width = 7.52, height = 4.56, units = "in")

```


```{r interactive_chart_ffc}

# plotly

Q_prob_plotly <- Q_pp %>%
  ggplot(aes(x = (1-plot_p), y = Q)) +
  geom_point(aes(x = (1-plot_p), y = Q, color = "Empirical"),
             shape = 16, size = 1.5) +
  stat_function(fun = qualn3, args = list(unname(q.evfit.fxd.param$ln3)), 
                aes(color = "Lognormal"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quape3, args = list(unname(q.evfit.fxd.param$pe3)), 
                aes(color = "Pearson Type III"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quawei, args = list(unname(q.evfit.fxd.param$wei)), 
                aes(color = "Weibull (EV III) - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = qua_ev, args = list(distribution = "gev", 
                                          para = q.evfit.fxd.param$gev), 
                aes(color = "GEV (max) - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = qua_ev, args = list(distribution = "gum", 
                                          para = q.evfit.fxd.param$gum), 
                aes(color = "Gumbel (EV I - max) - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quaglo, args = list(unname(q.evfit.fxd.param$glo)), 
                aes(color = "GLO"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = quanor, args = list(unname(q.evfit.fxd.param$nor)), 
                aes(color = "Normal - LM"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  stat_function(fun = qlpearsonIII, args = lpe3_param_list,
                aes(color = "Log Pearson III"), show.legend = T,
                size = 1, geom = "line", alpha = 0.5) +
  theme_bw(base_size = 10) +
  scale_x_log10(name = "Non-exceedance probability", 
                limits = c(0.01, 1),
                labels = scales::number_format(accuracy = 0.01)
  ) + 
  scale_y_log10(name = paste0("Annual peak flow  (m<sup>3</sup>/s)"), 
                limits = c(log_lower, log_upper), #adjust limits accordingly
                labels = scales::number_format(accuracy = 1)
  ) +
  scale_colour_manual("Distributions",
                      values = c("Empirical" = "black", 
                                 "Pearson Type III" = "blue2",
                                 "Log Pearson III" = "purple",
                                 "Normal - LM" = "maroon3",
                                 "Lognormal" = "orange", 
                                 "Gumbel (EV I - max) - LM" = "magenta",
                                 "GEV (max) - LM" = "red", 
                                 "Weibull (EV III) - LM" = "cyan3",
                                 "GLO" = "green3")) +
  theme(text=element_text(family=font_family, 
                          color="grey20", 
                          size = 12),
        legend.position = "right") +
  labs(title = paste0("Flood frequency curve"))



ggplotly(Q_prob_plotly,
         width = 800, height = 500) 

```

# Quantile-Quantile Plot

```{r static_chart_qqplot, fig.show = 'hide'}

#QQ PLOT

#calculate quantiles

qq_df <- Q_pp %>% 
  mutate(pe3 = quape3(f=(1-plot_p), para= q.evfit.fxd.param$pe3),
         #lpe3 = quaLPE3(f=(1-plot_p), para= parLPE3),
         lpe3 = qlpearsonIII(p=(1-plot_p), parLPE3[["mu"]], parLPE3[["sigma"]], parLPE3[["gamma"]]),
         nor = quanor(f=(1-plot_p), para= q.evfit.fxd.param$nor), 
         ln3 = qualn3(f=(1-plot_p), para= q.evfit.fxd.param$ln3),
         gum = qua_ev(distribution = "gum", f=(1-plot_p), para = q.evfit.fxd.param$gum),
         gev = qua_ev(distribution = "gev", f=(1-plot_p), para = q.evfit.fxd.param$gev),
         wei = quawei(f=(1-plot_p), para= q.evfit.fxd.param$wei),
         glo = quaglo(f=(1-plot_p), para= q.evfit.fxd.param$glo))

#pivot
qq_df2 <- qq_df %>% 
  pivot_longer(cols = -c(1:6),
               names_to = "dist",
               values_to = "theory_q") 
#select columns
qq_df2 <- qq_df2[,c(2,7:8)]

#replace distribution names
qq_df3 <- qq_df2 %>% 
  mutate(dist2 = dist)
qq_df3 <- qq_df3 %>% 
  mutate(dist2 = replace(dist2, dist == "pe3", "Pearson Type III"),
         dist2 = replace(dist2, dist == "lpe3", "Log Pearson III"),
         dist2 = replace(dist2, dist == "nor", "Normal - LM"),
         dist2 = replace(dist2, dist == "ln3", "Lognormal"),
         dist2 = replace(dist2, dist == "gum", "Gumbel (EV I - max) - LM"),
         dist2 = replace(dist2, dist == "gev", "GEV (max) - LM"),
         dist2 = replace(dist2, dist == "wei", "Weibull (EV III) - LM"),
         dist2 = replace(dist2, dist == "glo", "GLO"))
         
         

#chart
Q_QQ_plot <- qq_df3 %>%
  ggplot() +
  geom_point(aes(x = theory_q, y = Q, color = dist2,
                 text = paste0("Distribution: ", dist2,
                               "<br>Empirical quantile: ", sprintf("%0.1f", Q),
                               " m<sup>3</sup>/s<br>Theoretical quantile: ",
                               sprintf("%0.1f", theory_q),
                               " m<sup>3</sup>/s")),
             shape = 16, size = 1.5, alpha = 0.7) +
  geom_abline(intercept = 0, slope = 1) +
  theme_bw(base_size = 10) +
  scale_x_continuous(name = "Theoretical quantiles",
                     labels = comma,
                     limits = c(0, NA)
  ) + #x axis format
  scale_y_continuous(name = "Empirical quantiles",
                     labels = comma,
                     limits = c(0, NA) #adjust limits accordingly
  ) +
  scale_colour_manual("Distributions",
                      values = c("Empirical" = "black", 
                                 "Pearson Type III" = "blue2",
                                 "Log Pearson III" = "purple",
                                 "Normal - LM" = "maroon3",
                                 "Lognormal" = "orange", 
                                 "Gumbel (EV I - max) - LM" = "magenta",
                                 "GEV (max) - LM" = "red", 
                                 "Weibull (EV III) - LM" = "cyan3",
                                 "GLO" = "green3")) +
  theme(text=element_text(family=font_family, 
                          color="grey20", 
                          size = 10),
        axis.title = element_text(size = 8, colour = "gray35"),
        legend.position = "right") +
  labs(title = paste0("Quantile-quantile plot for annual peak flow"),
       subtitle = paste0(chart_subtitle),
       caption = paste0(chart_caption))

Q_QQ_plot

##print last plot to file
ggsave(paste0(new_dir, "/", filename2, "_QQplot.jpg"), dpi = 300,
       width = 7.52, height = 4.56, units = "in")

```


```{r interactive_chart_qqplot}

ggplotly(Q_QQ_plot,
         width = 800, height = 500) 

```
\newpage

# Evaluation

The results of the fit are evaluated using **Root Mean Square Error (RMSE)** to select the best probability distribution.

Rank the results by clicking on 'RMSE' column header.


```{r evaluation}

#EVALUATION
rmse_all <- qq_df3 %>% 
  group_by(dist2) %>% 
  summarise(RMSE = rmse(Q, theory_q))


#interactive table
#goodness-of-fit (RMSE)
reactable(rmse_all, 
          highlight = TRUE, striped = TRUE,
          columns = list(dist2 = colDef(name = "Distribution", align = "left"),
                         RMSE = colDef(align = "right", format = colFormat(digits = 2))))


```

# Quantile Estimation

```{r quantile_estimation}

#interactive table for quantile estimation

qT.evfit.fxd2 <- qT.evfit.fxd %>% 
  mutate(AEP = 1/RP*100)

qT.evfit.fxd3 <- qT.evfit.fxd2[,c(1,10,2:9)]

qT.evfit.fxd3 %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  mutate_all(~cell_spec(., "html", 
                        popover = spec_popover(content = paste0(qT.evfit.fxd3$RP, 
                                                                "-year flood value of ", .,
                                                                " m^3/s has a ", qT.evfit.fxd3$AEP,
                                                                "% chance of occuring in a single year"),
                                               title = NULL,  # title will add a Title Panel on top
                                               position = "right"
                        ),
                        color = ifelse(. < 0, "red"," black"))) %>%
  kable(digits = c(0,0,1,1,1,1,1,1,1,1), escape = F, format = "html", align = "r",
        format.args = list(big.mark = ","), #thousand separator, not working
        col.names = c("Return Period","AEP (%)","Lognormal", "Pearson Type III", "Weibull (EV III) - LM",
                      "GEV (max) - LM", "Gumbel (EV I - max) - LM", "GLO", "Normal - LM", "Log Pearson III")) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = T) %>%
  column_spec(1:2, bold = T, background = "gray80") %>% 
  column_spec(3:10, width = "3cm")


```

# AEP for given Flood

The table below shows the **Annual Exceedance Probability (AEP)** and **return period** of **`r flood_value` m^3^/s** flood for different probability distributions.


```{r AEP_given_Q}

#find return period/AEP given a flood value
dist_lf_all <- c("ln3", "pe3", "wei", "gev", "gum", "glo", "nor", "lpe3")

Calc_prob <- c(
  cdfln3(flood_value, para= q.evfit.fxd.param$ln3),
  cdfpe3(flood_value, para= q.evfit.fxd.param$pe3),
  cdfwei(flood_value, para= q.evfit.fxd.param$wei),
  cdf_ev(distribution = "gev", x = flood_value, para = q.evfit.fxd.param$gev),
  cdf_ev(distribution = "gum", x = flood_value, para = q.evfit.fxd.param$gum),
  cdfglo(flood_value, para= q.evfit.fxd.param$glo),
  cdfnor(flood_value, para= q.evfit.fxd.param$nor),
  plpearsonIII(flood_value, parLPE3[["mu"]], parLPE3[["sigma"]], parLPE3[["gamma"]])
)

AEP_flood <- data.frame(flood_value, dist_lf_all, (1-Calc_prob)*100)
names(AEP_flood) <- c("Flood", "Dist", "AEP")

AEP_flood <- AEP_flood %>% 
  mutate(RetPeriod = 1/AEP*100) %>% 
  mutate_at(vars(AEP), ~ round(., 2)) %>% 
  mutate_at(vars(RetPeriod), ~ round(., 0))

#replace distribution names
AEP_flood2 <- AEP_flood %>% 
  mutate(Distribution = Dist)
AEP_flood2 <- AEP_flood2 %>% 
  mutate(Distribution = replace(Distribution, Dist == "pe3", "Pearson Type III"),
         Distribution = replace(Distribution, Dist == "lpe3", "Log Pearson III"),
         Distribution = replace(Distribution, Dist == "nor", "Normal - LM"),
         Distribution = replace(Distribution, Dist == "ln3", "Lognormal"),
         Distribution = replace(Distribution, Dist == "gum", "Gumbel (EV I - max) - LM"),
         Distribution = replace(Distribution, Dist == "gev", "GEV (max) - LM"),
         Distribution = replace(Distribution, Dist == "wei", "Weibull (EV III) - LM"),
         Distribution = replace(Distribution, Dist == "glo", "GLO"))

AEP_flood3 <- AEP_flood2[,c(1,5,3,4)]

#interactive
reactable(AEP_flood3, 
          highlight = TRUE, striped = TRUE,
          columns = list(Flood = colDef(name = "Flood value (m^3/s)"),
                         Distribution = colDef(name = "Distribution", align = "left"),
                         AEP = colDef(name = "AEP (%)", align = "right", format = colFormat(digits = 2)),
                         RetPeriod = colDef(name = "Return Period (year)")))

```


```{r Excel_export}

###########################
#summary page
input_param <- c(
  'Station number',
  'Station name', 
  'Length of record (year)'
  )

input_value <- c(station_no,
                 station_name,
                 year_w_data)
input_page <- data.frame(cbind(input_param, input_value))


#list all dataframe
list_worksheet <- list("Input" = input_page,
                       "Prob" = Q_pp)


# Create a blank workbook
wb <- createWorkbook(creator = "Water Resources Unit, NAHRIM", title = version_no)

# Loop through the list of split tables as well as their names
#   and add each one as a sheet to the workbook
Map(function(data, name){
  addWorksheet(wb, name)
  writeData(wb, name, data)
}, list_worksheet, names(list_worksheet))




###########################
#insert data frames


#input flow data
writeData(wb, "Input", flowdata[c(1,2)], 
          startRow = 9, startCol = 1)
writeData(wb, "Input", "Flood Frequency Analysis 1.0", 
          startRow = 1, startCol = 1)
deleteData(wb, "Input", cols = 2, rows = 1, gridExpand = TRUE)



#Results
addWorksheet(wb, "Result")
writeData(wb, "Result", "Comparison of RMSE for all distributions", 
          startRow = 1, startCol = 1)
writeData(wb, "Result", rmse_all, 
          startRow = 2, startCol = 1)
writeData(wb, "Result", "Distributions", 
          startRow = 2, startCol = 1)

col_names <- c("Return Period (year)", "AEP (%)",
               "Lognormal", "Pearson Type III", "Weibull (EV III) - LM",
                "GEV (max) - LM", "Gumbel (EV I - max) - LM", "GLO", "Normal - LM", "Log Pearson III")
qT.evfit.fxd4 <- qT.evfit.fxd3
colnames(qT.evfit.fxd4) <- col_names

writeData(wb, "Result", "Quantile estimation", 
          startRow = 13, startCol = 1)
writeData(wb, "Result", qT.evfit.fxd4, 
          startRow = 14, startCol = 1)



#Flood
addWorksheet(wb, "Flood")
writeData(wb, "Flood", "AEP and Return Period for given flood", 
          startRow = 1, startCol = 1)
writeData(wb, "Flood", AEP_flood3, 
          startRow = 2, startCol = 1)
writeData(wb, "Flood", "Flood (m^3/s)", 
          startRow = 2, startCol = 1)
writeData(wb, "Flood", "AEP (%)", 
          startRow = 2, startCol = 3)
writeData(wb, "Flood", "Return period (year)", 
          startRow = 2, startCol = 4)


# formatting
##  create styles
###  title
title_style <- createStyle(fontName = "Tahoma", fontSize = 20, fontColour = "navyblue",
                           textDecoration = "bold")
addStyle(wb, "Input", style = title_style, rows = 1, cols = 1, stack = T)
### heading 1
head1_style <- createStyle(fontName = "Calibri", fontSize = 14, fontColour = "navyblue",
                           textDecoration = "bold")
addStyle(wb, "Result", style = head1_style, rows = 1, cols = 1, stack = T)
addStyle(wb, "Result", style = head1_style, rows = 13, cols = 1, stack = T)
addStyle(wb, "Flood", style = head1_style, rows = 1, cols = 1, stack = T)

### number and table border formatting
s_table <- createStyle(numFmt = "#,##0.0", border= "TopBottomLeftRight", borderColour = "gray48")
addStyle(wb, "Result", style = s_table, rows = 2:10, cols = 1:2, gridExpand = TRUE)
addStyle(wb, "Result", style = s_table, rows = 14:21, cols = 3:10, gridExpand = TRUE)
addStyle(wb, "Flood", style = s_table, rows = 2:10, cols = 1:4, gridExpand = TRUE)
s_table_AEP <- createStyle(numFmt = "0.00", border= "TopBottomLeftRight", borderColour = "gray48")
addStyle(wb, "Flood", style = s_table_AEP, rows = 2:10, cols = 3, gridExpand = TRUE)
s_table_RP <- createStyle(numFmt = "0", border= "TopBottomLeftRight", borderColour = "gray48")
addStyle(wb, "Flood", style = s_table_RP, rows = 2:10, cols = 4, gridExpand = TRUE)
s_table_text <- createStyle(border= "TopBottomLeftRight", borderColour = "gray48")
addStyle(wb, "Result", style = s_table_text, rows = 14:21, cols = 1:2, gridExpand = TRUE)

### word wrap
s_wrap <- createStyle(wrapText = T)
addStyle(wb, "Result", style = s_wrap, rows = 14, cols = 3:10, stack = T)
addStyle(wb, "Flood", style = s_wrap, rows = 2, cols = 1:4, stack = T)


#insert image
insertImage(wb, "Result", paste0(new_dir, "/", filename2, "_flood_freq_log.jpg"),  
            width = 7.52, height = 4.56, 
            startRow = 25, startCol = 1, units = "in")
insertImage(wb, "Result", paste0(new_dir, "/", filename2, "_flood_freq.jpg"),  
            width = 7.52, height = 4.56, 
            startRow = 25, startCol = 9, units = "in")
insertImage(wb, "Result", paste0(new_dir, "/", filename2, "_QQplot.jpg"),  
            width = 7.52, height = 4.56, 
            startRow = 50, startCol = 1, units = "in")


## set col widths
setColWidths(wb, "Input", cols = 1:2, widths = 20)
setColWidths(wb, "Result", cols = 1, widths = 25)
setColWidths(wb, "Flood", cols = 2, widths = 25)


###########################

# Save workbook to working directory
saveWorkbook(wb, file = paste0(new_dir, "/", filename2, "_flood_frequency.xlsx"), 
             overwrite = TRUE)

```



# References
